Fréchet Distance

### 2022-11-17 docs/paper.tex
basic point on line distance animation
wip: intro

\section{Introduction}
% motivation

% two (polygonal) curves

@@

However, this metric does not take the course of the curves into account. 
Two curves may be very dissimilar in the preception of a human 
but still have a small Hausdorff-distance, see \autoref{fig_hausdorff_distance_bad_example}.

@@

% TODO: Why allow it? Better algorithms?
The \textit{weak Fréchet distance} slightly modified the continuous version by allowing 
going backwards.

@@

\section{Algorithm}
% Original algorithm for the continuous Fréchet distance

% Free Space Diagram

% Runtime analysis (?)
% Correctness proof (?)

>>>>

\section{Introduction}
% motivation
At first it seems that measuring the similairty between two curves
is a very theoretical problem
but it has many, not that obvious, pratical applications.
It is used in Geo-Information-Systems (GIS) to 
quantify the similarity or quality of two maps, % cite
find patterns in vehicle traffic or animal tracking data 
by trajectory analysis, % cite
gesture recognition on touch devices like smartphones, % cite
and shape matching in the field of computer vision.

To quantify the similairty of two given curves (e.g. shapes, paths, or trajectories)
a distance metric can be used. 
We can't simply use a distance metric like eucledian distance 
becuase we don't want to compare points to points 
but instead compare curves to curves.

% two (polygonal) curves
% TODO: replace continous funcitons with other name
In the following we'll focus on polygonal curves (polygonal chains) 
instead of continuous functions ofen used in pure mathematics 
because most data we have for these problems is 
captured by some none continuous mechanisms, e.g., GPS positions from a tracking device.
Therefore we consider a polygonal curve $P$ to be definded as a 
sequence of points $p_1, \dots, p_n \in R^d$ where $d$ is the dimensionality 
of the space, e.g., $n=2$ or $n=3$, and linear interpolation between this points. 
However, many concepts also apply to continuous functions.

@@

However, this metric does not take the course of the curves into account. 
Two curves may have a small Hausdorff-distance but seem very dissimilar 
when looking at them, see \autoref{fig_hausdorff_distance_bad_example}.

@@

% TODO: Why allow it? Better algorithms?
The \textit{weak Fréchet distance} slightly modifies the continuous version by allowing 
going backwards.

@@

\section{Algorithms}
% Chapter summary and structure

\subsection{Original algorithm for the continuous Fréchet distance}
% Free Space Diagram
% Runtime analysis (?)
% Correctness proof (?)

\subsection{Improved Version?}

\subsection{Algorithms for different variants}
% discrete Fréchet distance

% weak Fréchet distance
